noam_data_exploration_v1

### 2024-07-19 noam_data_exploration_v3.Rmd
Codyn has a built in function to do what I want for temporal beta diversity but I can't run it (takes 13+ hr). Need to specify questions before subsetting.

>>>>

```{r multivariate change}
## Ran this for 13 hours and it didn't finish (obviously)
## Need to subset or specify questions or try remote access on more powerful computer
# multi_change_untransformed <-
#   multivariate_change(
#    df = long_data_sub,
#    time.var = "Year",
#    species.var = "Taxa",
#    abundance.var = "Percent_cover",
#    replicate.var = "Location"
#   )
#
